% !TEX root = main.tex

I would first like to thank my advisors Vinod Vaikuntanathan and Virginia Vassilesvka Williams. Thanks to Vinod for supporting me during my entire time at MIT, giving me the freedom to research what I was interested in and guidance along the way. Regardless of which topic I was looking into or thought I had a result for, he was excited about it and always made sure I understood all aspects of the proofs and background material. He taught me how to properly analyze and write up my results.

Special thanks to Virginia for mentoring me, and encouraging me to pursue new kinds of cryptography. Even though I studied a completely different subfield, we were able to find a lot of common ground. I learned so much during our meetings and developed a much bigger appreciation for complexity theory and algorithms, and their interplay with cryptography.

Next, a huge thanks to Tal Moran first for introducing me to Topology-Hiding Computation, and then being a supportive coauthor and mentor. Tal helped me find my stride as a researcher, teaching me how to expand on my research projects from one to the next. Because of him, I have a line of work exploring Topology-Hiding from multiple different models and angles. It has given me insight into multiparty computation as a field, and how to always be looking for the next question.

A thank you to Elette Boyle for hosting me in Israel, mentoring me, and being a great coauthor. Not only did she work with me on projects, she connected me to others during my time in Israel, introducing me to the community and to future collaborators. She also provided advice and feedback on how to approach research.

I also thank all of the rest of my coauthors: Adi Akavia, Marta Mularcyk, Chen-Da Liu, Daniel Tschudi, and Uieli Mauer. Among my coauthors, I would especially like thank Andrea Lincoln, who first suggested we be friends, and then work together, combining our fields. Andrea did not have any experience in cryptography, but her expertise in fine-grained complexity gave her a fresh perspective. Her perspective helped me notice my own blind-spots within the field, and inspired our first breakthrough result.

I would also like to thank my undergraduate research advisor, Dan Boneh. Without his initial support, I would not have pursued this field. I got my first taste of real cryptographic researching the summer of 2013, working with him and Manuel Sabin, and it was so much fun that I've never looked back. Dan continued to support me with research projects and directions for the rest of my undergrad career, and for that I thank him. It was a privilege to work with him.
I have continued to stay in touch with Manuel, and I thank him for sharing his perspectives on research, life, and beyond.

The theory group at MIT has been an important source of support for me during my time here. Thanks go to Gautam Kamath, Adam Sealfon, Sunoo Park, Madelina Persu, Cameron Musco, Chris Musco, Jerry Lee, and Dylan McKay. A thank you to the not-technically-a-theorist Thomas Bourgeat for playing music with us and sharing musings on math. A special thanks to Govind Ramnarayan for taking the time to not just teach me about different subfields, but also share thoughts on school, career, and life. Thanks also to Matt Staib for being an amazing friend in undergrad, and then continuing that friendship and support as a fellow student.

Other members of the crypto community have also been extremely helpful. I thank Yael Kalai for providing research direction and career guidance.
I also thank many members of the Northeastern Crypto group: Daniel Wichs, Ran Cohen, Ariel Hamlin, and Jack Doerner. I thank them for welcoming me into their community, reading groups, and other discussions.

Another group I cannot leave out of this section is the `Chicks of Course Six.' After meeting our first year in a networking seminar, we have met regularly for breakfast, sharing our journeys and supporting each other through the program. I thank all of them: Leilani Gilpin, Jelena Notaros, Jessica Ray, Marie Feng, Cecilia Testart, Sara Achour, and Candass Ross.

Finally, I would not have been able to do this without the support of my family. Thanks to Mom and Dad for visiting me, and talking me through the tough parts. I thank my sister, Ryan, for encouraging me, but also being blunt when I needed it. And thanks to Avery, my fianc\'e, for being here for me, helping me through all of the deadlines and travel, making the process infinitely more enjoyable.