\section{Introduction}

\xxx{Story: fine grained crypto needs all this stuff. }

Fine-grained complexity has helped explain the hardness of a wide variety of problems. 

The idea of fine-grained one way functions were introduced by Ball et.al. \cite{avgCaseFineGrained}. 

Fine-grained cryptography ideally would have all of the following objects listed bellow. Those in bold we have created. Those italicized have been solved previously. 

\begin{itemize}
	\item Plausibly average case hardness assumptions on which to base cryptographic constructions. 
	\begin{itemize}
		\item \textit{Worst case to average case reductions to show hardness for problems.} \cite{avgCaseFineGrained}
		\item Showing problems hard from satisfiability. 
		\item \textbf{Using plausible average case hypotheses. }
		\item Assumptions that have a fine-grained implications for quantum computers as well. 
	\end{itemize}
	\item  ``Symmetric'' Fine-grained Cryptography 
		\begin{itemize}
		\item \textbf{Fine-grained one way functions (FGOWFs)}
		\item \textbf{FGOWFs with hardcore bits}
		\item Fine-grained pseudo-random generators (FGPRGs)
		\end{itemize}
	\item ``Asymmetric'' Fine-grained Cryptography 
		\begin{itemize}
		\item Fine-grained trap-door functions
		\item \textbf{Fine-grained key transfer}
		\item Fine-grained public key cryptography
		\item Fine-grained identity based encryption
		\end{itemize}
	\item Advanced constructions
		\begin{itemize}
		\item Oblivious transfer
		\item Homomorphic encryption
		\end{itemize}
\end{itemize}